---
title: "The investigation of quality of weight lifting exercises"
author: "Andrey Bondarenko"
date: "26 Jul 2015"
output: html_document
---

Necessary libraries
-
```{r}
library(caret)
```

Data processing
-
Loading data:
```{r}
set.seed(79749)
training <- read.csv(url('http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv'))
testing  <- read.csv(url('http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv'))
```


There is a good function in the caret package that helps to remove variables with near zero variance:
```{r}
training <- training[, -nearZeroVar(training)]
```

Variables with many NA-values and id vector are also useless:
```{r}
NAs <- sapply(training, function(x) mean(is.na(x))) > 0.6
training <- training[,NAs==FALSE]
training <- training[c(-1)]
```

I divided given training data set into two additional parts:
```{r}
inTrain <- createDataPartition(y = training$classe, p = 0.6, list = FALSE)
my_training <- training[inTrain,]
my_testing  <- training[-inTrain,]
```

Model fitting
-
I used random forest model for given data, because it gave the best accuracy for prediction.
```{r}
modFit <- train(classe ~., method = "rf", data = my_training)
```

Generating confusion matrix:
```{r}
my_prediction <- predict(modFit, my_testing)
confusionMatrix(my_prediction, my_testing$classe)
```
So, the model has very good accuracy and low out-of-sample error.








